---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jpmap

<!-- badges: start -->
<!-- badges: end -->

jpmap provides geometry data of Japanese prefectures and layout functions in 
ggplot2.
The prefecture data in jpmap is based on the data provided by mapdata package.

## Installation

You can install the development version of jpmap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UchidaMizuki/jpmap")
```

## Example

`prefecture` contains geometry (sf) data of Japanese prefectures.

```{r, message=FALSE}
library(jpmap)
library(tidyverse)
library(sf)

prefecture
```

`layout_islands()` improves the layout of the Japanese islands in ggplot2 plots.

```{r}
plot <- ggplot(prefecture) +
  geom_sf()

plot
layout_islands(plot)
layout_islands(plot,
               ogasawara = FALSE)
```
